Illustrating Model Properties

### 2024-06-06 model.qmd
start with risk prediction figure(s)

>>>>

# Risk Predictions

Now, we want to make actual use of the model and predict the risk for occult diease given some diagnoses.

```{python}
import numpy as np
import matplotlib.pyplot as plt
from matplotlib import gridspec
from lyscripts.scenario import Scenario
from lyscripts.plot.utils import Histogram, draw, COLORS, split_legends
from scripts import paths, shared

all_false = {lnl: False for lnl in ["I", "II", "III", "IV", "V"]}

for i, t_stage in enumerate(["early", "late"]):
  for j, midext in enumerate([False, True]):
    contents = []
    for diagnosis in [
      {"III": True},
      all_false,
    ]:
      scenario = Scenario(
        t_stages=[t_stage],
        midext=midext,
        diagnosis={
          "ipsi": {"CT": diagnosis},  # Somehow, this does not seem to have any effect
          "contra": {"CT": all_false},
        },
        involvement={"contra": {"II": True}},
      )
      print(scenario.md5_hash("risks"))
      contents.append(
        Histogram.from_hdf5(
          filename=paths.model_dir / "full" / "risks.hdf5",
          dataname=scenario.md5_hash("risks"),
        )
      )
    draw(axes[i,j], contents, xlims=(0., 50.))

plt.savefig(paths.figure_dir / "fig-model-risks.png", dpi=400)
plt.show()
```
